---
title: "Test Platform for CensusGeocoder"
author: "Alan Jackson"
date: "July 15, 2018"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)
```

## Create test data

Create two test datasets, one that should work, and one with failure cases

```{r Test Data}

##  good

good_data <- c("10599 KIBER DR", "HOUSTON", "TX", "77031",
               "6499 ROOS RD", "HOUSTON", "TX", "77074",
               "1199 PIERCE ST", "HOUSTON", "TX", "77002",
               "5000 N Shepherd Dr", "Houston", "TX","77018",
               "5000 S Shepherd Dr", "Houston", "TX", "77098",
               "1000 E Tidwell Rd", "Houston", "TX", "77022",
               "1000 W Tidwell Rd", "Houston", "TX", "77091" 
               )
good_data <- cbind.data.frame(split(good_data, rep(1:4, times=length(good_data)/4)), stringsAsFactors=F)
names(good_data) <- c("address", "city", "state", "zip")

## bad

bad_data <- c( "3299 UNITY DR", "HOUSTON", "TX", "77057",
               "7499 MEMORIAL WOODS DR", "HOUSTON", "TX", "77024",
               "8699 LA FONTE ST", "HOUSTON", "TX", "77024",
               "6799 S BRAESWOOD BLVD", "HOUSTON", "TX", "77031",
               "1399 CHIMNEY ROCK RD", "HOUSTON", "TX", "77056",
               "999 LAMAR ST", "HOUSTON", "TX", "77002",
               "1699 PIERCE ST", "HOUSTON", "TX", "77003")

bad_data <- cbind.data.frame(split(bad_data, rep(1:4, times=length(bad_data)/4)), stringsAsFactors=F)
names(bad_data) <- c("address", "city", "state", "zip")

##Error in (function (..., row.names = NULL, check.rows = FALSE, check.names TRUE,  : 
##  arguments imply differing number of rows: 1, 0
##[1] "attempted 2"

```

##  Just the function Ma'am

The singular function, Census_decoder

Call sequence is

* address (required): street number and street name (1234 N Main ST)
* city (optional): City name. If both city and zip are given, they may conflict.
* state (optional): State 2-letter postal abbreviation
* zip (optional): 5 digit US Postal Zipcode

Either city and state, or zip is required


```{r census decoder}

Census_decoder <- function(address, city=NA, state=NA, zip=NA){
 
  #  required libraries 
  
  require(jsonlite)
  require(httr)
  
  print(paste(address, city, state, zip)) 
  urlreq <- paste0("https://geocoding.geo.census.gov/geocoder/geographies/address?street=",gsub(" ", "+",address))
  if (!is.na(city)){urlreq <- paste0(urlreq,"&city=", city)}
  if (!is.na(state)){urlreq <- paste0(urlreq,"&state=", state)}
  if (!is.na(zip)){urlreq <- paste0(urlreq,"&zip=", zip)}
  urlreq <- paste0(urlreq,"&benchmark=Public_AR_Current&vintage=Current_Current&format=json")
  print(paste("===>",urlreq))
  
  #   set up to retry twice on error (which usually works)
  attempt <- 1
  while(answer$status_code!=200 && attempt<=3 ) {
    if (attempt>1){print(paste("attempted", attempt))}
    attempt <- attempt + 1
    try(
      #     Go get result
      answer <- httr::GET(urlreq)
    )
  }
  #     did we succeed?
  
  ##############################
  r <- httr::GET(url_full)
  httr::stop_for_status(r)
  response <- httr::content(r)
  if (length(response$result$addressMatches) == 0) {
    message(paste0("Address (",
                   street, " ", city, " ", state,
                   ") returned no address matches. An NA was returned."))
    return(NA_character_)
  } else {
    if (length(response$result$addressMatches) > 1) {
      message(paste0("Address (",
                     street, " ", city, " ", state,
                     ") returned more than one address match. The first match was returned."))
    }
    return(response$result$addressMatches[[1]]$geographies$`Census Blocks`[[1]]$GEOID)
  }
  
  
  ##############################
  #lon <- as.character(json_file[["result"]][["addressMatches"]][["coordinates"]][["x"]])
  #lat <- as.character(json_file[["result"]][["addressMatches"]][["coordinates"]][["y"]])
  #block <-json_file[["result"]][["addressMatches"]][["geographies"]][["2010 Census Blocks"]][[1]][["BLOCK"]]
  #tract <- json_file[["result"]][["addressMatches"]][["geographies"]][["Census Tracts"]][[1]][["TRACT"]]
  #match_address <- json_file[["result"]][["addressMatches"]][["matchedAddress"]]
  
  #print(paste("output", lat, lon, block, tract, match_address))
  
  
  
}

```

##   Test function

```{r test function}

#---------------------------
# Good data - test with various optional pieces
#---------------------------

#  Full address

for (i in 1:nrow(good_data)) {
  #print(paste(i,"--->",good_data[i,]))
  test1 <- Census_decoder(good_data[i,]$address, 
                 good_data[i,]$city,
                 good_data[i,]$state)
  test2 <- Census_decoder(good_data[i,]$address, 
                 good_data[i,]$city,
                 good_data[i,]$state,
                 good_data[i,]$zip)
  test5 <- Census_decoder(address=good_data[i,]$address, 
                 zip=good_data[i,]$zip)
  print(test1)
  print(test2)
  print(test3)
  print(test4)
  print(test5)
}


```

